\begin{acknowledgments}
Before anything else, I would like to thank my parents, who not only believe in me, but also support whatever life choice I pursue, both emotionally and financially, something that not all parents can do.

I would like to express my deepest gratitude to the three C's: my advisor Carlton Caves, Christopher Ferrie, and Christopher Jackson,
%\footnote{All their first names begin with C! (not 100 factorial).}
without whom this dissertation would not have been possible.  It has been a valuable experience to be exposed to contrasting styles of mentoring, with Carl's high standards and emphasis on understanding explicit examples instead of getting caught up in generalities---a ``pedestrian approach" as he humbly puts it---on one hand, and Chris Ferrie's more whimsical, intuitive style on the other hand.  Although it has only been a year since I started collaborating with Chris Jackson, I always enjoy his presence and contagious passion on all things mathematical.  He also thoroughly read and gave a detailed feedback on every technical chapter of the dissertation. I would also like to thank the members of my dissertation committee: Carl, Chris Ferrie, Akimasa Miyake, Cristopher Moore, and Daniel Finley for taking time out of their busy schedules to read this dissertation.

My time at UNM has been one of the best times in my life, and everyone here is to be thanked for that. I have learned much from the faculty and post-docs in CQuIC (in addition to the three C's), especially Ivan Deutsch, Andrew Landahl, Akimasa Miyake, Cristopher Moore, Howard Barnum, Robin Blume-Kohout, Joshua Combes, and Rafael Alexander. It is also my pleasure to interact with other UNM faculty members, in particular, David Dunlap and Rouzbeh Allahverdi. My special thanks also go to fellow graduate students Jonathan Gross for just being an all-around brilliant groupmate, Jacob Miller for all the interesting random conversations, and Adrian Chapman and Qi Xiaodong for being officemates and surviving together. I thank Jonathan, Qi, Travis Scholten, and Anupam Mitra for organizing the outstanding computing workshop, and last but not least, the CQuIC Program Specialist, Gloria Cordova, for putting up with us and making our lives here easier.

I am indebted to Stephen Bartlett, Andrew Doherty, Steve Flammia, and everyone at the Quantum Science Research Group at the University of Sydney for the hospitality during my two visits.
\end{acknowledgments} 